Black-hole ringdown as a probe of higher-curvature gravity theories

### 2022-03-30 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
hs: more edits

@@

@@

We presented an unified framework to combine the parametrized formalism introduced
to model deviations to the GR QNMs~\cite{Maselli:2019mjd} with the \pSEOB~waveform model.
%
We showed through concrete examples how theory-specific calculations QNM of
slowly-rotating BHs in modified gravity theories can be mapped upon the
theory-agnostic beyond-GR parameters of the ParSpec formalism.
%
Together this allowed us to apply the \pSEOB~waveform model to test four
modified gravity theories (EdGB, dCS, cubic, and quartic
effective-field-theories of GR) using data from the GW events GW150914 and GW200129.
%
We found, in particular that, within the assumptions of our model and by
stacking posteriors, that the coupling constant of dCS gravity is bound to
$\ell_{\rm CS} \leqslant 34.5$~km.
%
In contrast, we could place any constraint of the coupling constants in EdGB gravity $\ell_{\rm GB}$.
%
This dichotomy between these theories has an analogy with works that considered
the inspiral part of the GW signal alone.
%
In that case, it is dCS which is unconstrained, while EdGB, in principle can be
constrained, based on results for the closely related shift-symmetric version
of this theory.

>>>>

We now consider the cubic EFT of GR, a case in which our results bear
similarity with what we found in dCS.

@@

Finally, let us consider the quartic EFT of GR.

@@

We presented an unified framework to combine the framework introduced
to model deviations to the GR QNMs~\cite{Maselli:2019mjd} with the \pSEOB~waveform model~\cite{Brito:2018rfr,Ghosh:2021mrv}.
%
We showed with concrete examples how theory-specific calculations QNM of
slowly-rotating BHs in modified gravity theories can be mapped onto the
theory-agnostic beyond-GR parameters of the ParSpec formalism.
%
Put together this allowed us to use the \pSEOB~waveform model to test four
modified gravity theories (EdGB, dCS, cubic, and quartic EFTs of GR) using
observational data from the GW events GW150914 and GW200129.
%
We found, in particular that, within the assumptions of our model and by
stacking posteriors, that the coupling constant of dCS gravity is bound to
$\ell_{\rm CS} \leqslant 34.5$~km.
%
In contrast, we could place any constraint of the coupling constants in EdGB gravity $\ell_{\rm GB}$.
%
This dichotomy between these theories has an analogy with works that considered
the inspiral part of the GW signal alone.
%
In that case, it is dCS which is unconstrained, while EdGB, in principle can be
constrained, based on results for the closely related shift-symmetric version
of this theory.
